%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Yusuf Ciger - Graduate Analyst
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[margin=0.7in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}

\titleformat{\section}
  {\large\bfseries\uppercase}
  {}
  {0em}
  {}
  [{\titlerule[0.5pt]}]

\titlespacing*{\section}{0pt}{10pt}{6pt}

\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill {\footnotesize #2} \\
  \textit{#3} \hfill \textit{#4}
  \vspace{4pt}
}

\begin{document}

\begin{center}
    {\Large \textbf{Yusuf Ciger}} \\[0.2cm]
    London, United Kingdom \textbar \quad
    +44 7909 653053 \textbar \quad
    ykerimciger@gmail.com \textbar \quad
    linkedin.com/in/yusuf-kerim-ciger
\end{center}

\vspace{-0.3cm}

\section{Professional Summary}

Analytical and systems-focused MSc Data Science graduate with experience improving operational workflows, automating reporting processes, and supporting data-driven decision making. Proven ability to identify inefficiencies, implement automation solutions, and collaborate with stakeholders to enhance system performance. Seeking to develop within a high-growth organisation as a Graduate Analyst.

\section{Key Skills}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Systems improvement and workflow optimisation
    \item Process automation and efficiency enhancement
    \item Data analysis and reporting for business decisions
    \item Stakeholder collaboration and requirement gathering
    \item SQL and structured data querying
    \item Python-based automation and data processing
\end{itemize}

\section{Professional Experience}

\entry{Sales Executive (Self-Employed, Interim Role)}{Mar 2026 -- Apr 2026}
{Customer Acquisition \& Field Sales}{London, UK}

\begin{itemize}[noitemsep, topsep=0pt]
    \item Took on a self-employed role upon relocating to the UK to gain immediate exposure to a fast-paced, customer-facing environment.
    \item Engage directly with customers to communicate value propositions and convert interest into agreements in a target-driven setting.
    \item Adapt communication approach in real-time based on customer behaviour, improving conversion outcomes.
    \item Developed strong objection-handling, resilience and persuasion skills through high-volume daily interactions.
\end{itemize}

\vspace{6pt}

\entry{Software Development Engineering Intern}{Jun 2023 -- Aug 2023}
{Amadeus}{Istanbul, Turkey}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Identified inefficiencies in a manual CI/CD reporting workflow used by analysts and redesigned the process using Python-based automation.
    \item Reduced manual reporting effort by 80\% by implementing automated data extraction and validation pipelines.
    \item Developed structured Excel reporting outputs to support faster operational decision-making.
    \item Collaborated with analysts to gather requirements and improve reporting accuracy and usability.
    \item Improved overall process efficiency by 30\% through workflow redesign and automation.
\end{itemize}

\vspace{6pt}

\entry{Teaching Assistant -- Introduction to Data Science}{Feb 2024 -- May 2024}
{Sabanci University}{Istanbul, Turkey}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Delivered structured analytical sessions to 30+ students, improving problem-solving capabilities.
    \item Provided feedback on data analysis approaches, enhancing structured thinking and interpretation.
    \item Supported coordination between academic staff and students to maintain consistent learning outcomes.
\end{itemize}

\vspace{6pt}

\entry{Product Management Intern}{Jul 2022 -- Sep 2022}
{Up2Us (Charity)}{Remote}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Analysed programme performance data to identify improvement areas and support decision-making.
    \item Assisted in tracking project milestones and maintaining structured delivery processes.
    \item Contributed to workflow coordination within a small, cross-functional team environment.
\end{itemize}

\vspace{6pt}

\entry{ERP Intern}{Jul 2020 -- Aug 2020}
{KEY Holding}{Istanbul, Turkey}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Supported ERP-based order and inventory processes to improve operational visibility.
    \item Generated structured shipment reports to enhance tracking accuracy across teams.
\end{itemize}

\section{Education}

\entry{MSc Data Science (Distinction)}{2024 -- 2025}
{University of Sussex}{Brighton, UK}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Applied data analysis and modelling techniques to support structured decision-making.
    \item Developed automated data pipelines and forecasting models.
\end{itemize}

\vspace{6pt}

\entry{BSc Computer Science and Engineering}{2019 -- 2024}
{Sabanci University}{Istanbul, Turkey}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Built strong foundation in databases, systems design, and process optimisation.
\end{itemize}

\section{Technical Tools}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Python (automation, data processing)
    \item SQL / MySQL (data querying)
    \item Microsoft Excel (reporting and analysis)
\end{itemize}

\section{Additional Information}

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1.5em]
    \item Full right to work in the UK (Graduate Visa, no sponsorship required)
    \item Languages: Turkish (Native), English (Fluent), French (Intermediate)
\end{itemize}

\end{document}
